---
title: "Accurate inference of genetic ancestry from cancer-derived sequencing"
author: Pascal Belleau, Astrid Deschênes and Alexander Krasnitz
output:
  rmarkdown::html_document:
    highlight: pygments
    toc: true
    fig_width: 5
    number_sections: true
pkgdown:
  asis: true
bibliography: aics.bibtex
vignette: >
  %\VignetteIndexEntry{Accurate inference of genetic ancestry from cancer-derived sequencing}
  %\VignettePackage{aics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r style, echo = FALSE, results = 'asis', warning=FALSE, message=FALSE}
BiocStyle::markdown()

suppressPackageStartupMessages({
  library(knitr)
  library(aics)
})

set.seed(121444)
```

# Licensing 

TODO

<br>
<br>

# Citing

If you use this package for a publication, we would ask you 
to cite the following:

TODO

# Installation

To install the latest version accessible on the 
[aics Github Website](https://github.com/adeschen/aics "aics Github Site"), 
the `r CRANpkg("devtools")` package is required.

```{r installDemo01, eval=FALSE}
## Load required package
library(devtools)

## Install the latest version of aics
devtools::install_github('adeschen/aics')
```

It is also possible to install an official release. The list of available 
releases is posted on the [aics Release Website](https://github.com/adeschen/aics/releases "aics Release Site").


```{r installDemo02, eval=FALSE}
## Load required package
library(devtools)

## Install the version v0.1.4 of aics
## using 'ref' parameter
devtools::install_github('adeschen/aics', ref = "v0.1.4")
```

<br>
<br>

# Introduction

Recent large-scale genomic studies of cancer point to differences 
in the molecular make-up of the disease among groups of different ancestral 
background. So, there is need for more molecular data to power discovery of 
such differences. 

<br>
<br>

# Session info

Here is the output of `sessionInfo()` on the system on which this document was 
compiled:

```{r sessionInfo, echo=FALSE}
sessionInfo()
```

<br>
<br>
